\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Publications},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\title{Publications}
\date{}

\begin{document}
\maketitle

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{J. Chen} and E. L. Severson

  \begin{itemize}
  \tightlist
  \item
    \href{https://github.com/horychen/Publications/blob/master/2019-Chen.Severson-Design.pdf}{\textbf{Design
    and modeling of the bearingless induction motor}}
  \item
    2019 IEEE International Electric Machines and Drives Conference
    (IEMDC),
  \item
    May 2019.
  \end{itemize}
\item
  \textbf{J. Chen} and J. Huang

  \begin{itemize}
  \tightlist
  \item
    \href{https://github.com/horychen/Publications/blob/master/2018-Chen.Huang-Globally\%20LyReg\%20-\%20Early\%20Access\%20Version.pdf}{\textbf{Globally
    Stable Speed-Adaptive Observer with Auxiliary States for Sensorless
    Induction Motor Drives}}
  \item
    IEEE Transactions on Power Electronics, vol.~34, no. 1,
  \item
    Jan 2019.
  \end{itemize}
\item
  \textbf{J. Chen}, J. Huang and Y. Sun

  \begin{itemize}
  \tightlist
  \item
    \href{https://github.com/horychen/Publications/blob/master/2018-Chen.Huang.ea-Resistances\%20-\%20Early\%20Access.pdf}{\textbf{Resistances
    and Speed Estimation in Sensorless Induction Motor Drives Using a
    Model with Known Regressors}}
  \item
    IEEE Transactions on Industrial Electronics, vol.~66, no. 4,
  \item
    April 2019.
  \end{itemize}
\item
  \textbf{J. Chen} and J. Huang

  \begin{itemize}
  \item
    \href{https://github.com/horychen/Publications/blob/master/2018-Chen.Huang-Application\%20EA\%2008454267.pdf}{\textbf{Application
    of Adaptive Observer to Sensorless Induction Motor Via
    Parameter-dependent Transformation}}
  \item
    IEEE Transactions on Control Systems Technology, doi:
    10.1109/TCST.2018.2863668,
  \item
    \begin{enumerate}
    \def\labelenumii{\arabic{enumii}.}
    \setcounter{enumii}{2018}
    \item
    \end{enumerate}
  \end{itemize}
\item
  \textbf{J. Chen} and J. Huang

  \begin{itemize}
  \tightlist
  \item
    \href{https://github.com/horychen/Publications/blob/master/2017-Chen.Huang-Stable\%20EMFState\%20Early\%20Access\%20Version.pdf}{\textbf{Stable
    Simultaneous Stator and Rotor Resistances Identification for Speed
    Sensorless Induction Motor Drives: Review and New Results}}
  \item
    IEEE Transactions on Power Electronics, vol.~33, no. 10,
    pp.~8695-8709,
  \item
    Oct 2018.
  \end{itemize}
\item
  \textbf{J. Chen} and J. Huang

  \begin{itemize}
  \tightlist
  \item
    \href{https://github.com/horychen/Publications/blob/master/2017-Chen.Huang-Online\%20EA.pdf}{\textbf{Online
    Decoupled Stator and Rotor Resistances Adaptation for Speed
    Sensorless Induction Motor Drives by a Time-division Approach}}
  \item
    IEEE Transactions on Power Electronics, vol.~32, no. 6,
    pp.~4587-4599,
  \item
    June 2017.
  \end{itemize}
\item
  \textbf{J. Chen}, J. Huang, and M. Ye

  \begin{itemize}
  \tightlist
  \item
    \href{https://github.com/horychen/Publications/blob/master/2017-Chen.Huang.ea-Totally.pdf}{\textbf{Totally
    Adaptive Observer for Speed Sensorless Induction Motor Drives:
    Simply a Cost of Extra Energy Consumption}}
  \item
    IEEE International Electric Machines and Drives Conference (IEMDC).
  \item
    May 2017.
  \end{itemize}
\item
  L. Zhao, J. Huang, \textbf{J. Chen}, and M. Ye

  \begin{itemize}
  \tightlist
  \item
    A Parallel Speed and Rotor Time Constant Identification Scheme for
    Indirect Field Oriented Induction Motor Drives
  \item
    IEEE Transactions on Power Electronics, vol.~31, no. 9,
    pp.~6494-6503,
  \item
    Sept 2016.
  \end{itemize}
\item
  T. Wang, J. Huang, M. Ye, \textbf{J. Chen}, W. Kong, M. Kang, and M.
  Yu

  \begin{itemize}
  \tightlist
  \item
    An EMF Observer for PMSM Sensorless Drives Adaptive to Stator
    Resistance and Rotor Flux-Linkage
  \item
    IEEE Journal of Emerging and Selected Topics in Power Electronics,
    doi: 10.1109/JESTPE.2018.2865862.
  \item
    2019
  \end{itemize}
\item
  Wang, T., Huang, J., Lin, B., Kang, M., \textbf{Chen, J.}, \& Kong, W.

  \begin{itemize}
  \tightlist
  \item
    \href{https://github.com/horychen/Publications/blob/master/wt-2019-eccentricity.pdf}{\textbf{Eccentricity
    detection of a six-phase induction motor with HFI}}
  \item
    IET Electric Power Applications.
  \item
    2019
  \end{itemize}
\end{enumerate}

\end{document}
